RJObject Paper

### 2014-06-21 Documents/Paper/ms.tex
Proposal for N

\subsection{Proposals that modify $N$}
The first kind of proposal we consider are proposals that change the
dimension of the model, i.e. proposals that change the value of $N$. By
necessity, these will also change the parameters $\{x_i\}_{i=1}^N$ because
the number of parameters will be changed.

>>>>

\subsection{Proposals that modify $N$}
The first kind of proposal we consider are proposals that change the
dimension of the model, i.e. proposals that change the value of $N$. By
necessity, these will also change the parameters $\{x_i\}_{i=1}^N$ because
the number of parameters will be changed. The proposals used here are
traditionally called {\it birth and death} proposals.

We will assume that the prior for $N$ is a discrete uniform distribution
between 0 and some $N_{\rm max}$, inclusive. The proposal starts by choosing
a new value $N'$ according to
\begin{eqnarray}
N' &=& \textnormal{mod}\left(N + \delta_N, N_{\rm max} + 1\right)
\end{eqnarray}
where $\delta_N$ is drawn from a heavy tailed
distribution.
